Empirical study of land surface effects on local rainfall

### 2018-09-04 Manuscripts/chap3_paper_WVversion.Rnw
changes for paper

## tree cover data
  mod44_tc <- brick("Data\\Satellite\\MOD44\\B\\mod44_tc_aus.tif")
  tm <- seq(as.Date("2000-03-06"), as.Date("2010-03-06"), "year")
  mod44_tc <- setZ(mod44_tc, tm, "year")

>>>>

## tree cover data
  mod44_tc <- brick("Data\\Satellite\\MOD44\\B\\mod44_tc_aus.tif")
  tm <- seq(as.Date("2000-03-06"), as.Date("2016-12-06"), "year")
  mod44_tc <- setZ(mod44_tc, tm, "year")

### 2018-09-04 Manuscripts/chap3_paper_new.Rnw
changes for paper

## extract sign of C
  C30_qld <- unlist(lapply(1:length(coef.rain30.qld4),
    function(x) ifelse(summary(coef.rain30.qld4)[x,2]=="gam",
                       summary(coef.rain30.qld4[[x]])$p.coeff[2],
                       NA)))
  C30_nswvic <- unlist(lapply(1:length(coef.rain30.nswvic),
    function(x) ifelse(summary(coef.rain30.nswvic)[x,2]=="gam",
                       summary(coef.rain30.nswvic[[x]])$p.coeff[2],
                       NA)))

Cp30_qld4 <- unlist(lapply(1:length(coef.rain30.qld4),
   function(x) ifelse(summary(coef.rain30.qld4)[x,2]=="gam",
                      summary(coef.rain30.qld4[[x]])$p.pv[2],NA)))
Cp30_nswvic <- unlist(lapply(1:length(coef.rain30.nswvic),
    function(x) ifelse(summary(coef.rain30.nswvic)[x,2]=="gam",
                       summary(coef.rain30.nswvic[[x]])$p.pv[2],
                       NA)))

>>>>

## extract sign of C
  C30_qld <- unlist(lapply(1:length(coef.rain30.qld4),
    function(x) ifelse(summary(coef.rain30.qld4)[x,2]=="gam",
                       summary(coef.rain30.qld4[[x]])$p.coeff[2],
                       NA)))
  C30_nswvic <- unlist(lapply(1:length(coef.rain30.nswvic),
    function(x) ifelse(summary(coef.rain30.nswvic)[x,2]=="gam",
                       summary(coef.rain30.nswvic[[x]])$p.coeff[2],
                       NA)))
# p-value of C
Cp30_qld4 <- unlist(lapply(1:length(coef.rain30.qld4),
   function(x) ifelse(summary(coef.rain30.qld4)[x,2]=="gam",
                      summary(coef.rain30.qld4[[x]])$p.pv[2],NA)))
Cp30_nswvic <- unlist(lapply(1:length(coef.rain30.nswvic),
    function(x) ifelse(summary(coef.rain30.nswvic)[x,2]=="gam",
                       summary(coef.rain30.nswvic[[x]])$p.pv[2],
                       NA)))
